---
title: "Indoor Navigation"
output: html_document
author: Christian Terbeck & Benjamin Dietz
---

```{r setup, include=FALSE}
```

```{r}
rawdata <- read.csv(file="/Users/benni/Downloads/studien_rohdaten2.csv", header=TRUE, sep=";")
```

In the following we use these abbreviation for the two studies:

 - MS-study - mobile standalone study - study that compares the stand-alone mobile indoor navigation system with the initial stationary kiosk system
 - MWK-study - mobile with kiosk system study - study that compares the system that combines the a kiosk system with a mobile navigation system with the initial stationary kiosk system

Deviding the dataset for the both user studies:
```{r}
ms_study = rawdata[rawdata$Verwendetes.System..2. == "Dietz", ]
mwk_study = rawdata[rawdata$Verwendetes.System..2. == "Terbeck", ]
```

The number of participants for the MS-study is `r length(ms_study[,1])` while `r length(mwk_study[,1])` people conducted the MWK-study.

# Functions

### Functions for SBSOD:
Calculating SBSOD for each person of the study:
```{r}
recodeSantaBarbara <- function(values) {
  x = c()
  for (i in values) {
    x = append(x, c(switch(i,7,6,5,4,3,2,1)))
  }
  return (x)
}
getSenseOfDirectionForPerson <- function(index, dataset) {
  sum = recodeSantaBarbara(dataset[,7])[index] + dataset[,8][index] + recodeSantaBarbara(dataset[,9])[index] + 
    recodeSantaBarbara(dataset[,10])[index] + recodeSantaBarbara(dataset[,11])[index] + dataset[,12][index] + 
    recodeSantaBarbara(dataset[,13])[index] + dataset[,14][index] + recodeSantaBarbara(dataset[,15])[index] + dataset[,16][index] + dataset[,17][index] + dataset[,18][index] + dataset[,19][index] + recodeSantaBarbara(dataset[,20])[index] + dataset[,21][index] 
  return (sum/15)
}
getAllSenseOfDir = function(dataset) {
  x = c()
  for (i in 1:length(dataset[,7])) {
    x = append(x, c(getSenseOfDirectionForPerson(i,dataset)))
  }
  return(x)
}
```

### Functions for NASA-TLX:
Calculating SBSOD for each person of the study:
```{r}
getNasaTLXPersonKonkol = function(dataset, i) {
  konkol = dataset[,29][i] + dataset[,30][i] + dataset[,31][i] + dataset[,32][i] + dataset[,33][i] + dataset[,34][i]
  return (konkol/6)
}

getNasaTLXPersonComparedSystem = function(dataset, i) {
  comparedSys = dataset[,45][i] + dataset[,46][i] + dataset[,47][i] + dataset[,48][i] + dataset[,49][i] + dataset[,50][i]
  return (comparedSys/6)
}

getAverageTLXComparedSystem = function(dataset) {
  persons = length(dataset[,1])
  sum = 0
  for (i in 1:persons) {
    sum = sum + getNasaTLXPersonComparedSystem(dataset, i)
  }
  return(sum/persons)
}

getAverageTLXKonkol = function(dataset) {
  persons = length(dataset[,1])
  sum = 0
  for (i in 1:persons) {
    sum = sum + getNasaTLXPersonKonkol(dataset, i)
  }
  return(sum/persons)
}

getAllTLXKonkol = function(dataset) {
  persons = length(dataset[,1])
  all = c()
  for (i in 1:persons) {
    all = append(all, getNasaTLXPersonKonkol(dataset, i))
  }
  return(all)
}

getAllTLXComparedSystem = function(dataset) {
  persons = length(dataset[,1])
  all = c()
  for (i in 1:persons) {
    all = append(all, getNasaTLXPersonComparedSystem(dataset, i))
  }
  return(all)
}

getAverageValue = function(dataset, column) {
  persons = length(dataset[,column])
  sum = 0
  for (i in 1:persons) {
    sum = sum + dataset[,column][i]
  }
  return(sum/persons)
}

```



# MS-study

### Participants
- `r length(ms_study[,2][ms_study[,2] == 1])` female and `r length(ms_study[,2][ms_study[,2] == 2])` male participants
- the age of the participant was between `r min(summary(ms_study[,3]))` and `r max(summary(ms_study[,3]))` with a mean value of `r mean(summary(ms_study[,3]))`
- `r length(ms_study[,6][ms_study[,6] == 1])` have never been in the building before while `r length(ms_study[,6][ms_study[,6] == 2])` have already been in the building but has no good knowledge about it ("Ich war schonmal hier, kenne mich aber nicht gut aus")

Background of participants:

 - natural science: `r length(ms_study[,4][ms_study[,4] == 1])`
 - medicine: `r length(ms_study[,4][ms_study[,4] == 2])`
 - social sciences: `r length(ms_study[,4][ms_study[,4] == 3])`
 - law: `r length(ms_study[,4][ms_study[,4] == 4])`
 - languages & culture: `r length(ms_study[,4][ms_study[,4] == 5])`
 - didactic: `r length(ms_study[,4][ms_study[,4] == 6])`
 - other: `r length(ms_study[,4][ms_study[,4] == 7])`

### SBSOD
Using the methods we introduced above, the participants of the study had the following SBSODs:
```{r}
getAllSenseOfDir(ms_study)
```

While these values range from `r min(getAllSenseOfDir(ms_study))` to `r max(getAllSenseOfDir(ms_study))`, the mean SBSOD value is `r mean(getAllSenseOfDir(ms_study))`.

### Smartphone and navigation usage of users

```{r}
ms_study[,25][ms_study[,25] == 1] <- "weekly"
ms_study[,25][ms_study[,25] == 2] <- "less than once a week"
ms_study[,25][ms_study[,25] == 3] <- "less than once a month"
ms_study[,25][ms_study[,25] == 4] <- "only in exception / emergency "
ms_study[,25][ms_study[,25] == 5] <- "never"
barplot(table(ms_study[,25]), main = "How often do participants use navigation systems in their everyday life?", xlim = c(0,5))
```

```{r}
pie(table(ms_study[,26]),labels=c("Yes","No"), main="I have already used an Indoor navigation system")
```

```{r}
pie(table(ms_study[,27]),labels=c("Yes","No"), main="I am familiar with scanning QR codes")
```


```{r}
mean(ms_study[,22])
barplot(table(ms_study[,22]), main = "The use of smartphones is very easy for me", sub ="1: strongly agree; 5: do not agree at all", xlim = c(0,5))
```

```{r}
mean(ms_study[,23])
barplot(table(ms_study[,23]), main = "I easily get lost in complex buildings", sub ="1: strongly agree; 5: do not agree at all", xlim = c(0,5))
```

```{r}
mean(ms_study[,24])
barplot(table(ms_study[,24]), main = "I cope well with new mobile apps", sub ="1: strongly agree; 5: do not agree at all", xlim = c(0,5))
```


### Time spend for the interaction

These are the times spend for the interaction with the system:
```{r}
ms_study$Zeit.Benutzung..1. # times of standalone mobile system
ms_study$Zeit.Benutzung..2. # times of initial kiosk system
```
|               | Standalone Mobile system           | Initial stationary system  |
|---------------|:----------------------------------:|---------------------------:|
| min value     | `r min(ms_study$Zeit.Benutzung..1.)` s                       |  `r min(ms_study$Zeit.Benutzung..2.)` s                     |
| max value     | `r max(ms_study$Zeit.Benutzung..1.)` s                       |  `r max(ms_study$Zeit.Benutzung..2.)` s                     |
| mean value   | `r mean(ms_study$Zeit.Benutzung..1.)` s                       |  `r mean(ms_study$Zeit.Benutzung..2.)` s                     |

### Time spend for the navigation

These are the times spent for the navigation with the system:
```{r}
ms_study$Zeit.Navigation..in.Sekunden...1. # times of standalone mobile system
ms_study$Zeit.Navigation..in.Sekunden...2. # times of initial kiosk system
```
|               | Standalone Mobile system           | Initial stationary system  |
|---------------|:----------------------------------:|---------------------------:|
| min value     | `r min(ms_study$Zeit.Navigation..in.Sekunden...1.)` s                       |  `r min(ms_study$Zeit.Navigation..in.Sekunden...2.)` s                     |
| max value     | `r max(ms_study$Zeit.Navigation..in.Sekunden...1.)` s                       |  `r max(ms_study$Zeit.Navigation..in.Sekunden...2.)` s                     |
| mean value   | `r mean(ms_study$Zeit.Navigation..in.Sekunden...1.)` s                       |  `r mean(ms_study$Zeit.Navigation..in.Sekunden...2.)` s                     |

### NASA TLX:

Initial kiosk system:
```{r}
summary(getAllTLXKonkol(ms_study))
```

Mobile system:
```{r}
summary(getAllTLXComparedSystem(ms_study))
```

### Overview: Evaluation of system
```{r}
dataset = ms_study
getMeanValue <- function(dataset, index) {
  return(round(mean(dataset[,index]), 2))
}
vergleich <- matrix(c(getMeanValue(dataset, 35), getMeanValue(dataset, 36),getMeanValue(dataset, 37), getMeanValue(dataset, 38),getMeanValue(dataset, 39), getMeanValue(dataset, 40), getMeanValue(dataset, 41), getMeanValue(dataset, 51), getMeanValue(dataset, 52), getMeanValue(dataset, 53), getMeanValue(dataset, 54),getMeanValue(dataset, 55), getMeanValue(dataset, 56),getMeanValue(dataset, 57)),ncol=7,byrow=TRUE)
colnames(vergleich) <- c("The system was easy to use","The system was good to understand", "I always felt that I was being well guided", 
                         "The system helped me to reach my destination reliably", "The system supported my orientation", "Would recommend to other people", "Would also use in other buildings")
rownames(vergleich) <- c("Konkol","Dietz")
vergleich
```


NASA TLX:
```{r}
rawdata = ms_study

mean(rawdata[,29][!is.na(rawdata[,29])]) # Mental demand: Konkol
mean(rawdata[,45][!is.na(rawdata[,45])]) # Mental demand: Dietz

mean(rawdata[,30][!is.na(rawdata[,30])]) # Physical demand: Konkol
mean(rawdata[,46][!is.na(rawdata[,46])]) # Physical demand: Dietz

mean(rawdata[,31][!is.na(rawdata[,31])]) # Temporal demand: Konkol
mean(rawdata[,47][!is.na(rawdata[,47])]) # Temporal demand: Dietz

mean(rawdata[,32][!is.na(rawdata[,32])]) # Performance: Konkol
mean(rawdata[,48][!is.na(rawdata[,48])]) # Performance: Dietz

mean(rawdata[,33][!is.na(rawdata[,33])]) # Effort: Konkol
mean(rawdata[,49][!is.na(rawdata[,49])]) # Effort: Dietz

mean(rawdata[,34][!is.na(rawdata[,34])]) # Frustration: Konkol
mean(rawdata[,50][!is.na(rawdata[,50])]) # Frustration: Dietz

```




# MWK-study

### Participants
- `r length(mwk_study[,2][mwk_study[,2] == 1])` female and `r length(mwk_study[,2][mwk_study[,2] == 2])` male participants
- the age of the participant was between `r min(summary(mwk_study[,3]))` and `r max(summary(mwk_study[,3]))` with a mean value of `r mean(summary(mwk_study[,3]))`
- `r length(mwk_study[,6][mwk_study[,6] == 1])` have never been in the building before while `r length(mwk_study[,6][mwk_study[,6] == 2])` have already been in the building but has no good knowledge about it ("Ich war schonmal hier, kenne mich aber nicht gut aus")

Background of participants:

 - natural science: `r length(mwk_study[,4][mwk_study[,4] == 1])`
 - medicine: `r length(mwk_study[,4][mwk_study[,4] == 2])`
 - social sciences: `r length(mwk_study[,4][mwk_study[,4] == 3])`
 - law: `r length(mwk_study[,4][mwk_study[,4] == 4])`
 - languages & culture: `r length(mwk_study[,4][mwk_study[,4] == 5])`
 - didactic: `r length(mwk_study[,4][mwk_study[,4] == 6])`
 - other: `r length(mwk_study[,4][mwk_study[,4] == 7])`

### SBSOD
Using the methods we introduced above, the participants of the study had the following SBSODs:
```{r}
getAllSenseOfDir(mwk_study)
```

While these values range from `r min(getAllSenseOfDir(mwk_study))` to `r max(getAllSenseOfDir(mwk_study))`, the mean SBSOD value is `r mean(getAllSenseOfDir(mwk_study))`.

### Smartphone and navigation usage of users

```{r}
mwk_study[,25][mwk_study[,25] == 1] <- "weekly"
mwk_study[,25][mwk_study[,25] == 2] <- "less than once a week"
mwk_study[,25][mwk_study[,25] == 3] <- "less than once a month"
mwk_study[,25][mwk_study[,25] == 4] <- "only in exception / emergency "
mwk_study[,25][mwk_study[,25] == 5] <- "never"
barplot(table(mwk_study[,25]), main = "How often do participants use navigation systems in their everyday life?", xlim = c(0,5))
```

```{r}
pie(table(mwk_study[,26]),labels=c("Yes","No"), main="I have already used an Indoor Navigation system")
```

```{r}
pie(table(mwk_study[,27]),labels=c("Yes","No"), main="I am familiar with scanning QR codes")
```


```{r}
mean(mwk_study[,22])
barplot(table(mwk_study[,22]), main = "The use of smartphones is very easy for me", sub ="1: strongly agree; 5: do not agree at all", xlim = c(0,5))
```

```{r}
mean(mwk_study[,23])
barplot(table(mwk_study[,23]), main = "I easily get lost in complex buildings", sub ="1: strongly agree; 5: do not agree at all", xlim = c(0,5))
```

```{r}
mean(mwk_study[,24])
barplot(table(mwk_study[,24]), main = "I cope well with new mobile apps", sub ="1: strongly agree; 5: do not agree at all", xlim = c(0,5))
```


### Time spend for the interaction

These are the times spent for the interaction with the system:
```{r}
mwk_study$Zeit.Benutzung..1. # times of standalone mobile system
mwk_study$Zeit.Benutzung..2. # times of initial kiosk system
```
|               | Standalone Mobile system           | Initial stationary system  |
|---------------|:----------------------------------:|---------------------------:|
| min value     | `r min(mwk_study$Zeit.Benutzung..1.)` s                       |  `r min(mwk_study$Zeit.Benutzung..2.)` s                     |
| max value     | `r max(mwk_study$Zeit.Benutzung..1.)` s                       |  `r max(mwk_study$Zeit.Benutzung..2.)` s                     |
| mean value   | `r mean(mwk_study$Zeit.Benutzung..1.)` s                       |  `r mean(mwk_study$Zeit.Benutzung..2.)` s                     |

### Time spend for the navigation

These are the times spend for the navigation with the system:
```{r}
mwk_study$Zeit.Navigation..in.Sekunden...1. # times of standalone mobile system
mwk_study$Zeit.Navigation..in.Sekunden...2. # times of initial kiosk system
```
|               | Standalone Mobile system           | Initial stationary system  |
|---------------|:----------------------------------:|---------------------------:|
| min value     | `r min(mwk_study$Zeit.Navigation..in.Sekunden...1.)` s                       |  `r min(mwk_study$Zeit.Navigation..in.Sekunden...2.)` s                     |
| max value     | `r max(mwk_study$Zeit.Navigation..in.Sekunden...1.)` s                       |  `r max(mwk_study$Zeit.Navigation..in.Sekunden...2.)` s                     |
| mean value   | `r mean(mwk_study$Zeit.Navigation..in.Sekunden...1.)` s                       |  `r mean(mwk_study$Zeit.Navigation..in.Sekunden...2.)` s                     |

### NASA TLX:

Initial kiosk system:
```{r}
summary(getAllTLXKonkol(mwk_study))
```

Mobile system:
```{r}
summary(getAllTLXComparedSystem(mwk_study))
```
### Overview: Evaluation of system
```{r}
dataset = mwk_study
getMeanValue <- function(dataset, index) {
  return(round(mean(dataset[,index]), 2))
}
vergleich <- matrix(c(getMeanValue(dataset, 35), getMeanValue(dataset, 36),getMeanValue(dataset, 37), getMeanValue(dataset, 38),getMeanValue(dataset, 39), getMeanValue(dataset, 40), getMeanValue(dataset, 41), getMeanValue(dataset, 51), getMeanValue(dataset, 52), getMeanValue(dataset, 53), getMeanValue(dataset, 54),getMeanValue(dataset, 55), getMeanValue(dataset, 56),getMeanValue(dataset, 57)),ncol=7,byrow=TRUE)
colnames(vergleich) <- c("The system was easy to use","The system was good to understand", "I always felt that I was being well guided", 
                         "The system helped me to reach my destination reliably", "The system supported my orientation", "Would recommend to other people", "Would also use in other buildings")
rownames(vergleich) <- c("Konkol","Dietz")
vergleich
```


NASA TLX:
```{r}
rawdata = mwk_study

mean(rawdata[,29][!is.na(rawdata[,29])]) # Mental demand: Konkol
mean(rawdata[,45][!is.na(rawdata[,45])]) # Mental demand: Dietz

mean(rawdata[,30][!is.na(rawdata[,30])]) # Physical demand: Konkol
mean(rawdata[,46][!is.na(rawdata[,46])]) # Physical demand: Dietz

mean(rawdata[,31][!is.na(rawdata[,31])]) # Temporal demand: Konkol
mean(rawdata[,47][!is.na(rawdata[,47])]) # Temporal demand: Dietz

mean(rawdata[,32][!is.na(rawdata[,32])]) # Performance: Konkol
mean(rawdata[,48][!is.na(rawdata[,48])]) # Performance: Dietz

mean(rawdata[,33][!is.na(rawdata[,33])]) # Effort: Konkol
mean(rawdata[,49][!is.na(rawdata[,49])]) # Effort: Dietz

mean(rawdata[,34][!is.na(rawdata[,34])]) # Frustration: Konkol
mean(rawdata[,50][!is.na(rawdata[,50])]) # Frustration: Dietz

```